How has the Brazilian Amazon been constructed as a problem? An analysis of

### 2022-04-08 Draft_April_2022/Full_draft_20220401.rmd
First attemppt at adding codebook table to rmd file

With the codebook in hands, each one of the authors, separately, hand-coded the same set of 1007 randomly selected Amazonian statements. This amount refers to 50% of all the Amazon Statements identified. Inter-coder agreement for each of the four main categories was 85%, on average. For each non-matching coded observation, the co-authors discussed and sorted their disagreements. Statements that mention the stem "amazon", but are not about the Brazilian Amazon, for example, might a greeting to the Governor of the Amazonas, were coded as false positives. The manually coded data is then randomly divided into a training set, containing 80% of the hand-coded observations (806 observations), and a validation set, containing the remaining 20% of the hand-coded data (201 observations). The training set is used to train the supervised machine-learning model that automatically classifies observations and the validation set is used to make sure the model fit is appropriate.

>>>>

```{r codebook, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
codebook <- tibble::tibble('Problem Construction' = c("National Sovereignty", "Economic Integration",
                                                    "Social Development", "Environmental Conservation"),
                           Description = c("This code constructs the Amazon region and/or forest as an issue of national sovereignty. We understand claims of sovereignty as a particular problem-construction that touches on imaginaries of external threats to territory. Relatedly, we also understand sovereignty as raising concerns about wrong perspectives and criticism from foreign and non-state actors about governments’ actions related to the Brazilian Amazon. In all, it advances the view that the Amazon is Brazilian, foreign, and non-state presence in the region needs to be monitored closely.", "This code constructs the Amazon region and/or forest as an issue of economic integration. It advances the view that the Amazon needs to be developed and connected to the national economy. This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes.", "This code constructs the Amazon region and/or forest as an issue of social development. It advances the view that Amazon is full of citizens who should have their rights guaranteed. This refers to the construction of schools and universities (right to education), of hospitals (right to health), and of housing (right to house). This also includes guarantees of a dignified life with decent employment, access to water and sanitation, as well as access to electricity, internet, radio, and light. Finally, this includes referrals to culture and the right to vote.", "This code constructs the Amazon region and/or forest as an issue of conservation. This problem-construction focuses on the value of a standing forest and of the preserved ecosystem in the region. The conservationist narrative advances the view that Amazon should be preserved, deforestation should be halted, and the practices of indigenous and traditional populations should be maintained and fostered. It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created."),
                           Example = c("We can now walk the world and when we debate about the Amazon, we do not need to wait for questions, we are the ones who are going to say what we are doing in the Amazon. We do not need to keep on saying ‘the Amazon is ours’ just for saying it, people often say this without much conviction either. If the Amazon has been ours since Cabral (European discoverer of Brazil) stepped here, why do we now have to worry about the Amazon? (Lula 2008)", "", "", ""))
knitr::kable(codebook, "simple")
```

With the codebook in hands, each one of the authors, separately, hand-coded the same set of 1007 randomly selected Amazonian statements. This amount refers to 50% of all the Amazon Statements identified. Inter-coder agreement for each of the four main categories was 85%, on average. For each non-matching coded observation, the co-authors discussed and sorted their disagreements. Statements that mention the stem "amazon", but are not about the Brazilian Amazon, for example, might a greeting to the Governor of the Amazonas, were coded as false positives. The manually coded data is then randomly divided into a training set, containing 80% of the hand-coded observations (806 observations), and a validation set, containing the remaining 20% of the hand-coded data (201 observations). The training set is used to train the supervised machine-learning model that automatically classifies observations while the validation set is used to make sure the model fit is appropriate.
